\section{Arcane Training}
\textbf{Cost:} 100 CP\\
\textbf{Requirements:} -\\
\textbf{Passive, Repeatable, Source(300 Gold)}\\
You have gained basic knowledge about arcane matters. You can cast spells from a spell book. Retrieving and opening a spell book takes 4 AP.\\
You can also write spells into spellbooks by copying them from scrolls, other spellbooks and other forms of written spells. The value of such a spell writing is reflected in the source cost of the spell perk. Doing so requires the neccessary CP and takes 1 hour for every 100 CP. Each new spell takes 1 page in the spellbook. Higher levels of the same spell don't take any additional pages to learn. Instead, you have to train yourself for some time in casting that specific spell in order to increase its level. Some spells have variations. These are similar to levels, but require a new page in the spell book. When learning a variation of the spell, you automatically also learn the base version of the spell if you haven't yet, paying the same amount of CP and Gold, and taking the same amount of time as if you had copied the base version first, and then the variation.\\
You also gain the ability to feel the magical radiation in the air, and feel disturbances in its structure. This allows you to feel magic radiating from magical items or find ruptures in the magical weave, but it doesn't allow you to discern their nature and properties.\\
You can also memorize a number of spells equals to your Intellect. Spells that you have memorized do not require a spell book to be cast. You can change memorized spells by spending 1 hour consulting your Spell Books.\\
\\
Level Progression:\\
II: 500 CP, you can add 1d4 to associated checks\\
III: 1000 CP, you can add 2d4 to associated checks\\
IV: 5000 CP, you can add 3d4 to associated checks\\