\section{Balance}
\textbf{Cost:} 0\\
\textbf{Requirements:} -\\
\textbf{Passive, Repeatable}\\
You gain 50 balance points. A character can have between 0 and 100 Balance Points, with 0 meaning that you become "enraged", losing your ability to think rationally, and 100 meaning that you are "calmed", being in a state of complete calm.\\
Whenever taking damage, your balance points are reduced by the amount of damage taken.\\
You can increase your balance points by meditation. Meditating for one hour regenerates 1D6+Vitality balance points.\\
A \textbf{calmed} character can dodge attacks even if they exceed his Reaction Value, and dodging doesn't cost stamina for a calmed character.\\
An \textbf{enraged} character adds their Strength to any Strength-based attack damage. They lose their ability to do anything else than moving and attacking with melee, Strength-based weapon attacks. This means they also cannot dodge, block, or use attack-augmenting perks like Aimed Attack or Brutal Attack. They drop any wielded weapons that don't allow for such an attack and use their fists instead. They then move to the closest creature no matter if friend or foe and start trying to kill it (choosing at random if multiple creatures are the same distance away). While enraged, a character loses 1 point of stamina per AP, and when they fall unconscious they gain 50 Balance points. If an enraged character reaches 0 Health, they don't die immediately. Instead, any damage beyond 0 Health reduces their stamina. If they aren't healed until their rage ends, they die once they have regained balance points.\\
The GM can subtract from a character's Balance Points in certain situations, like when your character witnesses a loved one dying or being hurt.
\\
Level Progression:\\
II: 200 Gold, you become calmed when you have 90 Balance Points or more.\\
III: 1000 Gold, you become calmed when you have 75 Balance Points or more.\\
IV: 5000 Gold, you become calmed when you have 50 Balance Points or more.\\