\section{Disciple of Avior}
\textbf{Cost:} 0 CP\\
\textbf{Requirements:} - \\
\textbf{Passive, Repeatable}\\
You are a disciple of Avior. You gain 5 Piety Points. Once during Midday, you can pray to prepare Prayers you know. Every prayer needs a certain amount of Piety Points. You can equip higher level prayers only if you equip the lower levels. You can freely use equipped Prayers. You can also learn and use Wonders. Using a Wonder reduces your total Piety Points. If your Piety Points are reduced to an amount lower than the prayers you have equipped requre, you need to choose and unequip enough Prayers to be below or equals your total Prayer Points again.\\
\\
Avior is the god of humankind, civilization, huntsmen, war, farming, the sun and the hearth. You gain Piety Points by performing certain activities. Whenever an activity states to kill a certain creature, it also assumes that you can help killing that creature (by being part of a fight against it) or change the creature into something else (e.g. "Kill a criminal" could also mean arresting them and making sure they are punished and change their ways)\\
\\
\begin{itemize}
	\item Kill a Beast, Giant or Goblinoid: 1 Piety Point per Combat Level of said creature above yours
	\item Kill a Demon Whorshipper or demon: 2 Piety Points per Combat Level of said Creature
	\item Win a fight in which you are outnumbered: 2 Piety Points
	\item Win a fight in which you are outnumbered 2 to 1: 5 Piety Points
	\item Defend a farmer or other form of commoner: 2 Piety Points
	\item Perform a normal quest for a city or township: 2 Piety Points
	\item Help a city or township defend themselves against a threat: 5 Piety Points
	\item Help in building a city or township: 20 Piety Points
	\item Heal an innocent that has been injured or diseased: 2 Piety Points
	\item Give 100 Gold to a church of Avior, a city or township, a hunter's lodge or a farming community: 1 Piety Point
\end{itemize}

Level Progression:\\
II: 250 CP, You can add 1d4 to rolls for knowledge about the gods and divine beings, and for Prayers and Wonders\\
III: 500 CP, You can add 2d4\\
IV: 1000 CP, You can add 3d4\\