\section{Disciple of Irani}
\textbf{Cost:} 0 CP\\
\textbf{Requirements:} - \\
\textbf{Passive, Repeatable}\\
You are a disciple of Irani. You gain 5 Piety Points. Once during Midday, you can pray to prepare Prayers you know. Every prayer needs a certain amount of Piety Points. You can equip higher level prayers only if you equip the lower levels. You can freely use equipped Prayers. You can also learn and use Wonders. Using a Wonder reduces your total Piety Points. If your Piety Points are reduced to an amount lower than the prayers you have equipped requre, you need to choose and unequip enough Prayers to be below or equals your total Prayer Points again.\\
\\
Irani is the godess of nature, the ocean, womanhood, birth, freedom and crime. You gain Piety Points by performing certain activities. Whenever an activity states to kill a certain creature, it also assumes that you can help killing that creature (by being part of a fight against it) or change the creature into something else (e.g. "Kill a criminal" could also mean arresting them and making sure they are punished and change their ways)\\
\\
\begin{itemize}
	\item Kill a humanoid or construct: 1 Piety Point per Combat Level of said Creature above yours.
	\item Kill a Demon Whorshipper or demon: 3 Piety Points per Challenge of said Creature
	\item Defend a woman: 2 Piety Points
	\item Steal from or rob a rich person: 1 Piety Points per 100 Gold stolen
	\item Kill someone in their sleep: 2 Piety Points
	\item Defend a forest from being destroyed: 5 Piety Points
	\item Perform a normal quest for a dryad or other nature spirit: 2 Piety Points
	\item Help defend one of Irani's sacred woods: 5 Piety Points
	\item Help sanctifying a corrupted forest: 10 Piety Points
	\item Help a pregnant woman giving birth or perform a marriage: 3 Piety Points
	\item Give 100 Gold to a church of Irani, a druid's circle, a beggar or a thieves' guild: 1 Piety Point
\end{itemize}

Level Progression:\\
II: 250 CP, You can add 1d4 to rolls for knowledge about the gods and divine beings, and for Prayers and Wonders\\
III: 500 CP, You can add 2d4\\
IV: 1000 CP, You can add 3d4\\