\section{Disciple of Ebron}
\textbf{Cost:} 0 CP\\
\textbf{Requirements:} - \\
\textbf{Passive, Repeatable}\\
You are a disciple of Ebron. You gain 5 Piety Points. Once during Midday, you can pray to prepare Prayers you know. Every prayer needs a certain amount of Piety Points. You can equip higher level prayers only if you equip the lower levels. You can freely use equipped Prayers. You can also learn and use Wonders. Using a Wonder reduces your total Piety Points. If your Piety Points are reduced to an amount lower than the prayers you have equipped requre, you need to choose and unequip enough Prayers to be below or equals your total Prayer Points again.\\
\\
Ebron is the god of travel, merchants, justice, dragons, time and balance. You gain Piety Points by performing certain activities. Whenever an activity states to kill a certain creature, it also assumes that you can help killing that creature (by being part of a fight against it) or change the creature into something else (e.g. "Kill a criminal" could also mean arresting them and making sure they are punished and change their ways)\\
\\
\begin{itemize}
	\item Kill a criminal or an elemental: 1 Piety Point per Combat Level of said creature above yours
	\item Kill a Demon Whorshipper or demon: 2 Piety Points per Combat Level of said Creature
	\item Resolve a crime by finding the culprit and bringing them to justice: 3 Piety points
	\item Perform a normal quest for a merchant: 2 Piety Points
	\item Help a merchant or shop owner stay in business: 3 Piety Points
	\item Help a merchant start off their business: 5 Piety Points
	\item Kill an evil or corrupted dragon: 20 Piety Points
	\item Perform as a judge in a matter of crime or other judical manner: 5 Piety Points
	\item Defend a Psionic from being killed: 5 Piety Points
	\item Accompany a group of travelers, ensuring their save arrival at their destination (not including your own group): 2 Piety Points
	\item Give 100 Gold to a church of Prak, a group of merchants, a judical court, a group of Psionics or a dragon: 1 Piety Point
\end{itemize}

Level Progression:\\
II: 250 CP, You can add 1d4 to rolls for knowledge about the gods and divine beings, and for Prayers and Wonders\\
III: 500 CP, You can add 2d4\\
IV: 1000 CP, You can add 3d4\\