\section{Disciple of Prak}
\textbf{Cost:} 0 CP\\
\textbf{Requirements:} - \\
\textbf{Passive, Repeatable}\\
You are a disciple of Prak. You gain 5 Piety Points. Once during Midday, you can pray to prepare Prayers you know. Every prayer needs a certain amount of Piety Points. You can equip higher level prayers only if you equip the lower levels. You can freely use equipped Prayers. You can also learn and use Wonders. Using a Wonder reduces your total Piety Points. If your Piety Points are reduced to an amount lower than your total equipped prayers need, you need to choose and unequip enough Prayers to be below your total Prayer Points again.\\
\\
Prak is the god of noblemen, guardian of death, the creator of magic and the god of craftsmen. You gain Piety Points by performing certain activities. Whenever an activity states to kill a certain creature, it also assumes that you can help killing that creature (by being part of a fight against it) or change the creature into something else (e.g. "Kill a criminal" could also mean arresting them and making sure they are punished and change their ways)\\
\\
\begin{itemize}
	\item Kill an undead creature or a Necromancer: 1 Piety Points  per Combat Level of said Creature above yours.
	\item Kill a Demon Whorshipper or demon: 3 Piety Points per Challenge of said Creature
	\item Discover a long-lost piece of magical lore: 3 Piety Points
	\item Craft a magical Item: 1 Piety Point per 500 Gold of item's worth, round down
	\item Perform a normal quest for a rightful ruler: 3 Piety Points
	\item Help a rightful ruler keep their thrown: 5 Piety Points
	\item Help a rightful ruler regain their thrown: 10 Piety Points
	\item Perform a proper burial for a recently deceased creature: 1 Piety Point
	\item Give 100 Gold to a church of Prak, a Library, a Wizard's Academy, a Cemetary, or a Forge: 1 Piety Point
\end{itemize}

Level Progression:\\
II: 250 CP, You can add 1d4 to rolls for knowledge about the gods and divine beings, and for Prayers and Wonders\\
III: 500 CP, You can add 2d4\\
IV: 1000 CP, You can add 3d4\\