\section{Elemental Magic Training}
\textbf{Cost:} Varies (See Below)\\
\textbf{Requirements:} \\
\begin{itemize}
	\item Arcane Training I
	\item Arcane Training II
	\item Arcane Training III
\end{itemize}
\textbf{Passive, Repeatable}\\
You have trained in a specific magical element, and acquired some knowledge of its applications and effects.\\
\\
You can learn this perk multiple times, learning a different element every time. Elements are associated with and opposed to each other in circles. If you take this perk to train in a second or even third element of a circle, it is more costly to do so. The "Nihil" element counts as being part of every other circle, therefore making it harder to train in any other element.\\
\\
When casting a spell with an elemental modifier, you can add your Level to any associated checks.

Also, you can apply the element to any spell that has an "empty" elemental modifier, if the spell allows that for the specified element. For example, if an element doesn't have an associated damage type, but the element would alter the spell's damage type,  you can't use that element to alter the spell.\\
\\
\\
Level Progression\\
II: You can add your level and 1d4\\
III: You can add your level and 2d4\\
IV: You can add your level and 3d4\\
\\
Cost:\\
\rowcolors{2}{lightgray}{white}
\begin{tabular}{l | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm}}
	Level & First of circle & Second of circle & Third of circle & Fourth of circle \\ \hline
	I & 50 Gold & 150 Gold & 400 Gold & 700 Gold\\
	II & 250 Gold & 500 Gold & 900 Gold & 1500 Gold\\
	III & 600 Gold & 1200 Gold & 1800 Gold & 2500 Gold\\
	IV & 1500 Gold & 2400 Gold & 3500 Gold & 5000 Gold\\
\end{tabular}
\\
\\
\\
Elements:\\
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | p{2.5cm} | p{7.25cm}}
	Element & Magic, Damage & Description\\ \hline
	\multicolumn{3}{c}{Circle of Nil}\\ \hline
	Nihil & Nihilomancy, Nihilation & 	The elemental nothingness, whatever comes in touch with this element becomes annihilated. It is the counter-idea of all other elements, destroying matter and magical energies alike. It can dispel magic, destroy matter and energy and negate effects.\\
	
	\multicolumn{3}{c}{Circle of Phota}\\ \hline
	Light & Luxomancy, Radiation & The element of light, this element contains everything that produces or distorts light. It can create light sources, dazzling flashes or illusions.\\
	Darkness & Tenebromancy, None & 	Not just the absence of light, darkness is the polar opposite of both having light or casting a shadow. It can be manifested in areas of pure darkness in even the brightest of days, becoming invisible or contacting it's dark origins to call forth dark creatures into your service.\\
	Shadow & Umbromancy, None & The elemental shadow, it can be found wherever there is some form of matter and some light. The planets cast shadow onto themselves at night,  and those who master this element can bend, animate or use this element to their advantage.\\
	
	\multicolumn{3}{c}{Circle of Anima} \\ \hline
	Life & Vivromancy, None* & 	The state of being alive is fueled by the completeness of body, soul and mind. Whenever one of these energies is damaged, a Vivromancer, commonly also known as "Healing Mages" can repair those energies. However, the element has many more applications than mere healing. \\
	Death & Mortomancy, Necrose & Part of being alive is dying. Whenever living matter is damaged beyond repair, it becomes dead. As the polar opposite of life, this element serves as fuel for new life. Death Magic damages living beings and involves wilting, curses, and frightening images of the afterlife.\\
	Undeath & Necromancy, None & 	Sometimes, a creature can not die. This happens when one of their three essential parts - body, soul or mind - becomes animated beyond the grave. Such creatures are fueled by the element of undeath, and Necromancers are commonly those who create, call forth, or sometimes cleanse them from this energy. Undeath can raise and command undead, talk to the diseased or destroy undead creatures. \\
	
	\multicolumn{3}{c}{Circle of Motua}\\ \hline
	Lightning & Fulgomancy, Elecricity & 	Lightning is the result of an imbalance between positive and negative energies. Whenever such an imbalance is created, the omnipresent energy of balance in the universe creates an explosive, direct blast in which the imbalance collapses onto itself. Such an energy can damage living creatures and lifeless matter alike, but it can also be used to animate muscle fiber and increase its effectiveness. \\
	Cold & Frigomancy, Cold & 	In the absence of movement, negative energies are created. Water freezes, air drops to the ground and life dies. Cold can damage creatures, erode mountains and crystallize living matter.\\
	Heat & Pyromancy, Hot & In the overabundance of movement, positive energies are forced into being. Air rises, water evaporates into steam and living matter bursts into flame. Heat can damage living matter, melt stone and spread destruction and ash across the lands.\\
	
	\multicolumn{3}{c}{Circle of Materia}\\ \hline
	Water & Aquamancy, Corrosive* & The element of water is the element of balance between chaos and stasis. Whenever matter becomes movable and dynamic, it becomes fluid. Water, Lava, even Time, all of those things are moved by the arcane element of water. The acidic or basic alignment of any water-based material can corrode living matter and crystalline structures alike.\\
	Air & Aeromancy, Cutting* & Whenever a material enters a state of being dynamic beyond being fluid, it becomes gaseous, and starts being governed by the element of air. Air can keep breathing creatures alive in other elements, or can suffocate them with poisonous gas or by removing the oxygen from their lungs. When it is moved fast enough, it can cut skin and rend flesh. \\
	Earth & Terramancy or Geomancy, Blunt* & The element of crystalline, mineral, frigid structures is Earth. It is the polar opposite of both the dynamic air and the balanced water, and stands for immobility and stern resilience. It can crush others under its weight, build mountains and fortresses for eternity, and when it collides with something, only the strong survives.\\
\end{longtable}
\*Even though life has no associated damage type, some of its spells have curative power, usually referred to as "negative" damage which heals living creatures, but damages undead, as if it were a damage type.\\
\\
\*Even though the spells in the circle of materia have specific associated damage types, a lot of spells that have the modifiers from this circle deal different types of damage. \\