\section*{Read Mind}
\textbf{Cost:} 300 Gold\\
\textbf{Requirements:} -\\
\textbf{Element:}: Lightning\\
\textbf{Spell, Repeatable, Active, Source, Memory}\\
For 10 AP and 5 Mana, you can read the surface thoughts of a creature that you can see for 1 Minute. This does require your concentration. Make an Intellect check contested by their Vitality check. They can always add their level to this check. If you succeed, you understand their strongest current base emotion, so if they are angry, bored, scared, excited, content, hungry, thirsty, envious etc.\\
\\
This spell requires you to whisper a magical formula, so unless you are closer than 5 passus to the creature or they are watching you, they usually don't notice that you cast a spell on them. If they succeed against your Intellect check by 5 or more, they become aware of something trying to intrude their mind.\\
\\
Level Progression:\\
\\
II: 2000 Gold and Lightning Training I, you are able to understand surface thoughts of a creature for 20 Mana. Doing so gives them a +2 bonus on their vitality check against you. This includes their immediate plans and current state of mind. This means that you can react to their plans immediately, giving you an advantage of +4 on related checks (for example, dodging or blocking, detecting deceptions, haggling or discussions etc.)\\
\\
III: 5000 Gold and Lightning Training II, you are able to read someone's overall motivations and disposition for 50 Mana. Doing so gives them a +4 bonus on their vitality check against you. It means you can read their most basic desires, whom they call friends or foes, how they see you, what makes them tick etc. This gives you a +8 on any checks when interacting with said creature, but doesn't give an increased bonus on defensive checks in combat (it stays at +4 from reading their immediate plans).\\