\section{Telekinesis}
\textbf{Cost:} 100 CP\\
\textbf{Requirements:} -\\
\textbf{Element:} Air\\
\textbf{Spell, Active, Source, Memory, Repeatable}\\
You spend 6 AP and 5 Mana to slightly lift a remote object or creature that you can see and that is not heavier than one tenth your Intellect in stone. You can move the lifted item around freely in the air, taking 1 Mana and 1 AP per Passus moved. You can also just keep it in the air, which doesn't cost you AP or Mana.\\
The effect ends when you decide to, when you lose concentration or when you lose sight of the object. Another person can try to also control the same object. If they are doing so manually, they make a Strength check against your Intellect check. if they also try to manipulate the object with a Telekinesis spell, you make opposing Intellect checks similar to the effect of a "Dispel Magic" spell. If you lose, the spell also ends and the other person gains control of the item.\\
\\
Level Progression:\\
II: 500 CP, 10 initial Mana for on fifth your Intellect in stone.\\
III: 1000 CP, 20 initial Mana for one third your Intellect in stone. Also, moving lifted items that are lighter than one tenth your Intellect in stone doesn't cost Mana anymore\\
IV: 2500 CP, 30 initial Mana for half your Intellect in stone. Also, moving lifted items that are lighter than one fifth your Intellect in stone doesn't cost Mana anymore\\
V: 5000 CP, 40 initial Mana for your Intellect in stone. Also, moving lifted items that are lighter than one third your Intellect in stone doesn't cost Mana anymore\\
VI: 10000 CP, Moving lifted items that are lighter than half your Intellect in stone doesn't cost Mana anymore\\