\section{Odem Curse}\label{perk:odemCurse}
\textbf{Cost:} 100CP\\
\textbf{Requirements:} -\\
\textbf{Passive, Repeatable}\\
You were born with the power of Odem inside of you.
This allows you to train in the three flames of power, but also to gain other abilities as well.
However, Odem is not a gift, but a curse instead.
Whenever you would become heavily wounded, your willpower may explode in an invisible, violent force called a burstout.
Roll a D6. On an odd number, every creature in a \passus{20} radius around you must make a Vitality Check.
The DV of this check is your Empathy + 7 + your combined level, and they can add their combined level to the check if they also have the Odem Curse perk.
If they fail, they take 1d10 psychic damage per level you have (all three levels).\\
You then fall unconscious.\\
Your GM may also call for a D6 roll to check for a burstout if your character is under strong emotional duress, such as if one of your allies is harmed strongly.\\
If you rolled an even number on the D6, you do not suffer a burstout.\\
After your first burstout like this, a guild of specialized manhunters called "The Seekers", which is part of the Church of Four, becomes aware of you, and starts hunting for you.
Once they catch you and take you into custody, they seal your powers with an~\nameref{perk:odemSigil}.
\\
Rank Progression:\\
II: 500 CP, your burstout only deals 1d8 damage per level\\
III: 2,500 CP: your burstout only deals 1d6 damage per level\\
IV: 5,000 CP: your burstout only deals 1d4 damage per level\\
V: 10,000 CP: you have learned to control your burstouts, and they don't deal any damage anymore\\