\section{Consumables}\label{sec:consumables}
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r}
	Name & Size & Price (In Gold)\\ \hline
	Arrows (20) & M & 5\\
	Bolts (20) & M & 5\\
	Bandages & T & 5\\
	Candle & T & 5\\
	Ink & T & 10\\
	Ink, Magical & T & 50\\
	Inkpen & CS & 20\\
	Lantern Oil & T & 5\\
	Meal, Trail Ration & S & 3\\
	Grilled Meat & S & 5\\
	Simple Stew & S & 3\\
	Savory Porridge & S & 2\\
	Spell Scrolls & T & Varies\\
	Torch & S & 3\\
	Whetstone & T & 10\\
\end{longtable}


\textbf{Bandages} can be used increase natural healing.
When applying them, make a Dexterity check.
This counts as a check regarding medicine.
If your check is higher than the wounded person's Vitality, the person's natural healing is increased by 1 per hour for 8 hours.
A creature can only benefit from this if they are wounded or heavily wounded.\\

\textbf{Candles} keep an area of \passus{2} radius around them in dim light for up to 5 hours.
They are often used in rituals.\\

\textbf{Ink} comes in small vials and can fill up to 20 pages of paper with text.\\

\textbf{Ink, Magical} comes in small vials and can fill up to 5 pages in a spellbook or prayerbook.\\

\textbf{Inkpens} are necessary for writing.
With proper care, one inkpen can last a lifetime.\\

\textbf{Lantern Oil} comes in vials and can keep a lantern lit for up to 2 hours.\\

\textbf{Trail Rations} are a combination of dried and salted meats, double-baked bread and cheese.
One meal sets your hourly Mana regeneration to 1D6 Mana.\\

\textbf{Grilled Meat} is meat cooked over an open fire.
It sets your hourly Mana regeneration to 1d4+1 Mana, and gives the user +5 temporary health for the next 8 hours.\\

\textbf{Simple Stew} is a mixture of carbohydrates and meat simmered in a simple broth.
It sets your hourly Mana regeneration to 4 Mana, and gives the user +10 temporary stamina for the next 8 hours.\\

\textbf{Savory Porridge} is a base of carbohydrates with some meat or other protein for taste.
It is quite harty, giving the user +10 temporary stamina and +5 temporary health for the next 8 hours.
It also sets your hourly Mana regeneration to 1d4 Mana.\\

\textbf{Spell Scrolls} are a magically written form of a spell.
A character can use a Spell Scroll to cause the effect of a spell, requiring both the AP and Mana to cast it, even if they have not memorized it.
A character who has mastered the prerequisite rune perks to cast the spell can copy it into a spellbook, and memorize it from there.
The price of a Spell Scroll is equal to the Source cost of the spell it contains.

\textbf{Torches} last for one hour and shine bright light in a radius of \passus{3} and dim light for another \passus{3} beyond that.\\

\textbf{Whetstones} can be used to sharpen weapons that deal cutting damage.
Sharpening a weapon takes 10 minutes.
For the next 10 attacks after that, that weapon also deals a critical hit on a natural 19.
A whetstone can be used up to 10 times.\\