\section{Enchantments}

Enchantments can be placed on different types of equipment, like armor, rings or necklaces. Enchanting an item changes its value by the given amount, and requires the listed ingredients. Enchanting something usually takes 1 hour of time for every 100 gold that the resulting item is worth. If the Creation DV is failed by 5 or more, the ingredients - but not the enchanting target - are lost.\\


\subsection{Minor Enchantments}
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | p{2.5cm} | p{2.5cm}| l |l | l }
	Name & Target & Ingredients & DV & Value & Price\\ \hline
	Chilled & 1x Weapon or 10x Ammunition & 1x Cold Essence, 1x Tiny Soul Shard & 15 & +500 & 100\\
	Ember & 1x Weapon or 10x Ammunition & 1x Fire Essence, 1x Tiny Soul Shard & 15 & +500 & 100\\
	Sparking & 1x Weapon or 10x Ammunition & 1x Lightning Essence, 1x Tiny Soul Shard & 15 & +500 & 100\\
	Spell Scroll & 1x Empty Spell Scroll & Casting a Spell & 15 & Varies & 20\\
\end{longtable}

A weapon enchanted with \textbf{Chilled} deals +1 Cold damage per damage die. You can enchant a melee weapon, 10 units of ammunition or a ranged weapon, like a bow, crossbow or sling.\\


A weapon enchanted with \textbf{Ember} deals +1 Hot damage per damage die. You can enchant a melee weapon, 10 units of ammunition or a ranged weapon, like a bow, crossbow or sling.\\


A weapon enchanted with \textbf{Sparking} deals +1 Electrical damage per damage die. You can enchant a melee weapon, 10 units of ammunition or a ranged weapon, like a bow, crossbow or sling.\\


\textbf{Spell Scrolls} can be cretaed from spells you know. Doing so requires you to cast the spell upon it, which means you need to spend the neccesary time and mana. The resulting scroll has the level and element you chose. Casting from a scroll takes as long as casting the spell normally takes, but doesn't require someone to know the spell and doesn't require initial mana.