\section{Mundane Objects}
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r}
	Name & Weight & Price (In Gold)\\ \hline
	Backpack & 0.01 & 5\\
	Bedroll & 0.05 & 2\\
	Blanket & 0.01 & 1\\
	Chain, 2 passus & 0.05 & 20\\
	Crowbar & 0.01 & 10\\
	Fire Steel & - & 10\\
	Grappling Hook & 0.05 & 50\\
	Lantern & 0.05 & 100\\
	Lock, Very Easy (DV 15) & - & 10\\
	Lock, Easy (DV 20) & - & 50\\
	Lock, Medium (DV 25) & - & 100\\
	Lock, Hard (DV 30) & - & 500\\
	Lock, Very Hard (DV 35) & - & 1000\\
	Lockpick Set & - & 10\\
	Lockpick Set, Good & - & 100\\
	Lockpick Set, Great & - & 500\\
	Lockpick Set, Masterful & - & 1000\\
	Paper, per Page & - & 1\\
	Potion Belt, 3 Slots & - & 10\\
	Potion Belt, 5 Slots & - & 50\\
	Prayer Book & 0.01 & 50\\
	Rope, 10 passus & 0.03 & 50\\
	Shackles & 0.01 & 100\\
	Small Mirror & - & 100\\
	Spellbook & 0.01 & 50\\
	Tent & 0.1 & 10\\
	Waterskin & 0.25/- & 2\\
\end{longtable}



A \textbf{Backpack} can hold up to 5 stones worth of materials, provided they fit into it.\\

A \textbf{Bedroll} has enough room for one person and can be folded and attached to a backpack without actually removing space from it.\\

A \textbf{Blanket} keeps up to one person warm. In addition to a bedroll, it can be used to brave cold temperatures.\\

A \textbf{Chain} is made of interlocking iron rings and can be broken only by making a DV 35 Strength check.\\

A \textbf{Crowbar} awards +5 on checks to open crates, break down doors and windows etc.\\

\textbf{Fire Steel} is used in combination with flint (included) to create sparks. Creating a fire in this way doesn't require any checks, but still takes 5 minutes.\\

A \textbf{Grappling Hook} can be used in combination with a rope in order to scale featureless surfaces, as long as the user can hook it to something.\\

A \textbf{Lantern} sheds light in a 6 Passus Cone, and uses 1 vial of lantern oil per hour.\\

\textbf{Locks} can be attached to doors, chests, chains, etc. Each lock comes with a key when bought, and remaking a key costs half as much as the lock itself. The DV in brackets denotes how difficult it is to pick the lock.\\

\textbf{Lockpick Sets} contain multiple sets of lockpicks, as well as pryers and short pieces of metal wire. Higher quality lockpicks increase your chances of picking locks with them. While normal lockpick sets don't give any bonuses, good lockpick sets add +2, great lockpick sets add +4 and masterful lockpick sets add +6 to checks involving picking locks with them. Lockpick sets have a 1 in 10 chance of breaking if you roll a natural 1 on a check to pick a lock.

\textbf{Paper} can be written on. One piece of paper is considered to be 1 one sixteenth of a square passus large, so 25 * 25 fin.\\

A \textbf{Potion Belt} can be used to strap filled vials to a person's body. This removes the need to retrieve it from that person's backpack, making it far quicker to drink a potion.\\
	
A \textbf{Prayer Book} holds up to 100 spells, and requires magical ink to write something in it. A character casting a spell has to have that spell in their spellbook and recite it out of it.\\

A \textbf{Rope} comes in different strengths and can be used for various things.\\

\textbf{Shackles} can be used to bind a person. They come with one key, and making another key for a pair of shackles requires 20 gold.\\

A \textbf{Small Mirror}, made of steel and glass, can be used to reflect things. Has a handle that can be used to attach it to a stick with a notch.\\

A \textbf{Spellbook} holds up to 100 spells, and requires magical ink to write something in it. A character casting a spell has to have that spell in their spellbook and recite it out of it.\\

A \textbf{Tent} is made of skins and fabric and can hold up to 4 people, and can be hooked into the earth in order to withstand winds.\\

A \textbf{Waterskin} provides enough room for 5 Pugnus (0.25 stone) of fluid. In water, that is the amount a person needs to drink per day. When empty, it's considered to not weigh anything.\\