\section{Potions}
Potions can be used by drinking them. Drinking a potion takes 2 AP, and retrieving them from your inventory costs an additional 4 AP.

\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r}
	Name & Weight & Price (In Gold)\\ \hline
	Antidote & 0.05 & 30\\
	Health Potion & 0.05 & 100\\
	Mana Potion & 0.05 & 100\\
	Spider's Venom & 0.05 & 30\\
	Stamina Potion & 0.05 & 50\\
	Strength Potion & 0.05 & 50\\
	Vitality Potion & 0.05 & 50\\
	Agility Potion & 0.05 & 50\\
	Dexterity Potion & 0.05 & 50\\
	Intellect Potion & 0.05 & 50\\
	Perception Potion & 0.05 & 50\\
	Empathy Potion & 0.05 & 50\\
\end{longtable}


Drinking an \textbf{Antidote} grants a creature +4 on any checks against poison or venom effect for the next hour.\\

A \textbf{Health Potion} regenerates 2d6+2 Health immediately.\\

A \textbf{Mana Potion} regenerates 2d6+2 Mana immediately.\\

A \textbf{Spider's Venom} can be applied to any melee weapon that deals cutting or piercing damage. It can also be applied to a batch of up to 10 units of ammunition or thrown weapon. The effect lasts until the weapon strikes a creature, so it isn't wasted on a natural 1 or a dodge. However, a piece of ammunition or thrown weapon also loses the poison's properties on use, regardless if it hit a creature or not. Applied poison loses its effectiveness after 1 hour.\\
Applying a poison takes 1 minute and requires a DV 15 Dexterity check. On a failed check, the user loses the poison. If the check is failed by 5 or more the character is affected by the poison.\\
Someone hurt a weapon drenched in Spider's venom (so at least one damage was dealt) must make a DV 12 VIT check or take 3D6 Necrotic damage. If this damage would cause a wound, it instead reduces the victim's AGI by 1d4. A creature dropped to 0 AGI by that damage becomes paralyzed.\\

A \textbf{Stamina Potion} regenerates 2d6+2 Stamina immediately.\\

A \textbf{Strength Potion} increases your Strength by 1 for 1 hour.\\

A \textbf{Vitality Potion} increases your Vitality by 1 for 1 hour.\\

A \textbf{Agility Potion} increases your Agility by 1 for 1 hour.\\

A \textbf{Dexterity Potion} increases your Dexterity by 1 for 1 hour.\\

A \textbf{Intellect Potion} increases your Intellect by 1 for 1 hour.\\

A \textbf{Perception Potion} increases your Perception by 1 for 1 hour.\\

A \textbf{Empathy Potion} increases your Empathy by 1 for 1 hour.\\