\section{Ingredients}\label{sec:ingredients}
These are items that can be found and harvested in order to create items.
They are ordered by type.\\
\\

\subsection{Alchemical solvents}\label{subsec:solvents}
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | l}
	Name & Price (In Gold) & Effect\\ \hline
	Alcohol, cheap & 5 & Crafting Check -4\\
	Alcohol, mediocre & 10 & Crafting Check -2\\
	Alcohol, normal & 20 & Nothing\\
	Alcohol, fine & 50 & Crafting Check +2\\
	Alcohol, exquisite & 100 & Crafting Check +4\\
	Oil, cheap & 3 & Crafting Check -4\\
	Oil, mediocre & 7 & Crafting Check -2\\
	Oil, normal & 15 & Nothing\\
	Oil, fine & 40 & Crafting Check +2\\
	Oil, exquisite & 80 & Crafting Check +4\\
	Water, stale & - & Crafting Check -2\\
	Water, drinkable & -/1 & Nothing\\
	Water, spring & 5 & Crafting Check +2\\
	Water, distilled & 20 & Crafting Check +4\\
\end{longtable}

Prices for alcohol, oil and water don't include prices for bottles.
They are considered to be enough for one bottle, which equals 5 vials.
One vial full of alcohol, oil or water is needed for alchemical recipes. \\

The price for drinkable water depends on the area - buying the water from a tavern or a well-owner costs 1 gold per bottle, but otherwise it might be considered free.\\


\subsection{Soul Shards}\label{subsec:soulShards}
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r}
	Shard & Size & Price (In Gold)\\ \hline
	Tiny & CS & 50\\
	Small & CS & 250\\
	Normal & T & 1,000\\
	Large & T & 5,000\\
	Massive & T & 10,000\\
	Huge & S & 50,000\\
	Radiant & T & 100,000\\
\end{longtable}


\subsection{Alchemical Ingredients}\label{subsec:alchemicalIngredients}
Alchemical Ingredients contain certain essences.
If a recipe requires a specific essence, any item that contains that essence can be used for that potion.
Some potions may require different ingredients with the same essence, or very specific items. \\

\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r}
	Name & Size & Price (In Gold)\\ \hline
	Health Essence I & T & 20\\
	Body Essence I & T & 20\\
	Poison Essence I & T & 15\\
	Magic Essence I & T & 25\\
	Ice Essence I & T & 30\\
	Speed Essence I & T & 35\\
	Fire Essence I & T & 30\\
\end{longtable}

\subsection{Cooking ingredients}\label{subsec:cookingIngredients}
This is a list of ingredients that can be used in recipes.
If a recipe calls for a specific type of ingredient, any ingredient with that type can be used.
The effect of that item are then applied to the resulting meals.
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r | l | p{3cm} }
	Name & Size & Price (In Gold) & Type & Effect\\ \hline
	Bread, stale & T & 1 & Carbohydrate & None\\
	Bread, normal & T & 2 & Carbohydrate & +1 Mana\\
	Bread, good & T & 3 & Carbohydrate & +2 Mana\\
	Salt, sea or rock & CS & 2 & Season & None\\
	Salt, high quality & CS & 5 & Season & +1d4 Motivation\\
	Cheese, cheap & T & 1 & Side & None\\
	Cheese, fresh & T & 2 & Side & +5 temp Stamina\\
	Cheese, hard & T & 3 & Side & +10 temp Stamina\\
	Cheese, high quality & T & 10 & Side & +20 temp Stamina\\
	Meat, beef & T & 5 & Protein & +1d4 Motivation\\
	Meat, pork & T & 3 & Protein & None \\
	Meat, wolf & T & 8 & Protein & +1d8 temp Health\\
	Meat, giant spider & T & 10 & Protein & Meal lasts +2 weeks\\
\end{longtable}

Whenever a meal effect would result in temporary Stamina, Health or Mana, or give motivation dice, this effect lasts for 8 hours, or until the next meal is consumed.
After that, the effect ends.
Temporary Health and Mana are consumed first, temporary Stamina is consumed last.
Neither can be replenished after being used.
Motivation dice can be added on any attribute check, including attack and defense rolls.
The character using the motivation can decide if and how many motivation dice are spent on one check before making the roll.
The dice are spent afterwards and cannot be used again.\\

\subsection{Scraps}\label{subsec:scraps}
These resources can be collected from monsters or the environment.
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r }
	Name & Size & Price\\ \hline
	Wolf Fur Scraps & T & 2\\
	Leather Scraps & T & 1\\
	Bronze Scraps & T & 3\\
	Iron Scraps & T & 4\\
	Copper Scraps & T & 1\\
	Tin Scraps & T & 2\\
	Cloth Scraps & T & -\\
\end{longtable}

\subsection{Resources}\label{subsec:resources}
These resources can be bought or crafted from scraps and other resources.
\begin{longtable}{l | r | r }
	Name & Size & Price\\ \hline
	Feathers, 20 & T & 5\\
	Leather & S & 20\\
	Leather Fittings & S & 10\\
	Innards & T & 5\\
	Cloth & S & 5\\
	Yarn & T & 10\\
	Wolf Fur & S & 100\\
	Metal Fittings & S & 50\\
	Nail & T & 5\\
\end{longtable}

\subsection{Ingots}\label{subsec:ingots}
These metal ingots can be used for weapons, armor and other items.
Whenever such a recipe allows for multiple ingots, they have to be of the same type.
The effects listed are applied to any weapon, armor or other item crafted with this metal, respectively if the recipe itself calls for "metal ingot".
\begin{longtable}{l | r | r | p{2cm} | p{2cm} | p{2cm}}
	Name & Weight & Price (In Gold) & Armor & Weapon & Other\\ \hline
	Bronze Ingot & T & 30 & - & -1 Quality & -\\
	Iron Ingot & T & 60 & - & - & -\\
	Steel Ingot & T & 100 & +1 Cutting, +1 Piercing Res & Crit Range +1 & +30\% val\\
	Mithril  Ingot & T (but weighs like CS) & 500 & +1 Cutting, +1 Piercing, +2 max agility & +2 damage per die & value doubled, weight halved\\
\end{longtable}

