\section{Rage}\label{perk:rage}
\textbf{Cost:} 100 CP\\
\textbf{Requirements:} -\\
\textbf{Maneuver, Active, Repeatable}\\
You can enter a state of rage as part of an action.
While in rage, you gain a Rage Bonus to Strength of +1, as well as a Rage Bonus to Damage of +1 on Strength-based attacks, and +2 on two-handed Strength-based attacks.
Additionally, you gain an amount of Temporary Hit Points equal to your Vitality.
You can end your rage whenever you want, but it automatically ends after 1 Minute (30 AP) for every Rank of Rage you have.
While in rage, you lose 5 Stamina for every attack you make.
While in rage, you are immune to becoming~\nameref{condition:exhausted} or~\nameref{condition:heavilyExhausted}.
After you have raged, you become~\nameref{condition:heavilyExhausted} for 1 hour.
While exhausted in this manner, your Stamina are reduced to \sfrac{1}{10} of your maximum stamina.
You begin regaining stamina normally after one hour.
\\
Rank Progression:\\
II: 250 CP\\
You now gain double your Vitality as temporary Hit Points.\\
You now lose 4 Stamina for every attack you make.\\
The Strength bonus of your rage is now +2, and the damage bonus is now +2, or +4 for two-handed attacks.\\
The exhaustion after raging now lasts for only 50 Minutes.\\
\\
III: 750 CP\\
You now also gain a Rage Bonus to Damage Reduction of +1 against all damage types that would target your Health, except psychic.\\
You now lose 3 Stamina for every attack you make.\\
The Strength bonus of your rage is now +3, and the damage bonus is now +3, or +6 for two-handed attacks.\\
The exhaustion after raging now lasts for only 40 Minutes.\\
\\
IV: 1,500 CP\\
You now gain three times your Vitality as temporary Hit Points.\\
You now lose 2 Stamina for every attack you make.\\
The Strength bonus of your rage is now +4, and the damage bonus is now +4, or +8 for two-handed attacks.\\
The exhaustion after raging now lasts for only 30 Minutes.\\
\\
V: 3,500 CP\\
The damage reduction from your rage is now increased to +2\\
You now lose 1 Stamina for every attack you make.\\
The Strength bonus of your rage is now +5, and the damage bonus is now +5, or +10 for two-handed attacks.\\
The exhaustion after raging now lasts for only 20 Minutes.\\
\\
VI: 7,500 CP\\
Your rage now reduces your current Stamina, not your maximum stamina, after it has ended.\\
You now lose no additional Stamina for every attack you make.\\
The Strength bonus of your rage is now +6, and the damage bonus is now +6, or +12 for two-handed attacks.\\
The exhaustion after raging now lasts for only 10 Minutes.\\
\\