\section{Armor and Clothing}
Every character can wear an armor, a helmet, a set of gloves, a set of boots, two rings and one amulet or other type of necklace. Also, a character can wear one belt, which can house items that can be accesssed easily.

\subsection{Clothing}

Clothing in itself does not count as armor, but it does grant Armor Reduction.

While wearing clothing and robes, a character counts as "unarmored", meaning that they can add their level to defensive rolls.


\rowcolors{2}{lightgray}{white}
\begin{longtable}{p{1.5cm} | p{4cm} | p{2.5cm} | p{1cm} | p{1.5cm}}
	Name & Resistances & Description & Wght & Price\\ \hline
	Clothing (Different types) & 1 cutting, 2 cold, 2 heat & Just some normal clothing & 0 & 10\\
	
	Novice Robes & +1 Wound Threshold, 2 cold, 2 heat & A novice priest, monk or mages' robes & 0 & 10\\
	
	Mages' Robes & 2 cutting, 1 piercing, +3 Wound Threshold, 3 cold, 3 heat, 2 necrose, 2 radiation, 2 nihilation & A mages' robes. Magical & 0 & 600\\
	
	Priests' Robes & 2 cutting 1 piercing, +2 Wound Threshold, 3 cold, 3 heat, 2 corrosive, 2 radiation, 2 nihilation, 2 psychic & A priests' robes. Magical & 0 & 670\\
	
	Robes of Protection & 1 against every damage type, +1 Wound Threshold & Enchanted magical robes that look like standard monk's robes. Hard to attain. Magical & 0 & 2450\\
\end{longtable}


\subsection{Light Armor}

Light armor is flexible and allows agile users to move around freely. It can usually be donned and doffed in a matter of one or two minutes, and doesn't require a certain strength level to be worn. However, out of the three armor types, it also sports the least defense. Leather, fur and very light, but also very expensive metals or metal chains are used to create light armor.


\rowcolors{2}{lightgray}{white}
\begin{longtable}{p{1.5cm} | p{4cm} | p{2.5cm} | p{1cm} | p{1.5cm}}
	Name & Resistances & Description & Wght & Price\\ \hline
	
	Leather Byrnie & 1 blunt, 1 cutting, 1 piercing, +1 Wound Threshold & A short-sleeved leather shirt armor & 0,2 & 40 Gold\\ 
	
	Fur Byrnie & 1 cutting, 1 piercing, +2 Wound Threshold, 2 cold & A shirt made of different types of fur & 0,4 & 50 Gold\\
	
	Gambeson & 2 cutting, 1 piercing, +1 Wound Threshold, 2 cold, 2 hot & A quilted, long-sleeved hauberk made from cloth & 0,1 & 160 Gold\\
	
	Studded Leather Hauberk & 1 blunt, 2 cutting, 2 piercing, +2 Wound Threshold & A long-sleeved hauberk made from leather, studded with bronze plates. & 0,7 & 170 Gold\\
	
	Wolf Fur Byrnie & 2 cutting, 2 piercing, +3 Wound Threshold, 3 cold & A shirt made of wolf's fur. & 0,8 & 350 Gold\\
	
	Boiled Leather Cuirass & 1 blunt, 3 cutting, 2 piercing, +3 Wound Threshold & A cuirass made from hardened, boiled leather & 0,8 & 350 Gold\\
	
	Bear Fur Byrnie & 1 blunt, 3 cutting, 2 piercing, +4 Wound Threshold, 3 cold & A shirt made of a bear's fur & 1,1 & 1.090 Gold\\
	
	Salamander Leather Hauberk & 1 blunt, 5 cutting, 4 piercing, +5 Wound Threshold, 2 hot, 1 electrical & A long-sleeved top made from a salamander's hide & 0,4 & 5.730 Gold\\
	
	Iron Chain Shirt & 2 blunt, 5 cutting, 4 piercing, +5 Wound Threshold, 3 hot & A byrnie made from chain-linked rings of iron. & 0,8 & 13.560 Gold\\
	
	Steel Chain Shirt & 2 blunt, 6 cutting, 4 piercing, +5 Wound Threshold, 3 hot & A byrnie made from chain-linked rings of steel & 0,7 & 17.700 Gold\\
	
	Dragon Leather Hauberk & 2 blunt, 6 cutting, 5 piercing, +6 Wound Threshold, 2 cold, 4 hot, 2 corrosive & A long-sleeved top made of dragon leather & 0,4 & 26.920 Gold\\
	
	Wyrm Leather Cuirass & 3 blunt,	6 cutting, 6 piercing, +7 Wound Threshold, 4 cold, 6 hot, 4 corrosive, 5 electrical & A hard cuirass made from the hide of a great wyrm's hide. & 0,9 & 101.400 Gold\\
	
	Enchanted Mithril Plate & 2 against every damage type. +2  Wound Threshold & An enchanted cuirass made from the light mithril alloy. Magical & 0 & 101.900 Gold\\
\end{longtable}

\subsection{Medium Armor}

Medium Armor is a great balance between the strong defenses of heavy armor and the agility of light armor. It is often made of overlapping slabs of metal or hardened leather, to build "scale" armor. Some pieces of medium armor reduce the Agility of the wearer to a maximum value.


\rowcolors{2}{lightgray}{white}
\begin{longtable}{p{1.5cm} | p{4cm} | p{2.5cm} | p{1cm} | p{1.5cm}}
	Name & Resistances & Description & Wght & Price\\ \hline
	
	Cloth Scale Hauberk &
	2 blunt, 3 cutting, 1 piercing, +2 Wound Threshold, 2 cold, 2 heat &
	A long-sleeved hauberk made from cloth scales. &
	0,2 &
	1.800 \\
	
	Arctic Bear Fur Byrnie &
	1 blunt, 3 cutting, 2 piercing, +4 Wound Threshold, 4 cold &
	A shirt made from a polar bear's fur. Maximum 10 Agility &
	2,8 &
	1.950\\
	
	Leather Scale Hauberk &
	2 blunt, 4 cutting, 2 piercing, +3 Wound Threshold, 2 cold, 2 hot &
	A hauberk made from overlapping leather pieces. Maximum 10 Agility &
	0,6 &
	2.690\\
	
	Leather Brigandine &
	1 blunt, 4 cutting, 3 piercing, +4 Wound Threshold &
	A shirt made of quilted leather. &
	0,7 &
	2.390\\
	
	Iron Scale Hauberk &
	2 blunt, 5 cutting, 3 piercing, +4 Wound Threshold, 1 cold, 1 hot &
	A long-sleeved top adorned with overlapping iron plates. Maximum 10 Agility &
	2,7 &
	5.390\\
	
	Volcanic Glass Cuirass &
	2 blunt, 3 cutting, 1 piercing, +3 Wound Threshold, 1 cold, 3 hot, 6 corrosive, 2 radiation, 2 electricity &
	A cuirass made of hardened volcanic glass. Stiff, but nearly weightless. Maximum 10 Agility &
	0 &
	23.730\\
	
	Ironplate Brigandine &
	1 blunt, 4 cutting, 3 piercing, +3 Wound Threshold, 2 cold, 2 hot, 1 electricity &
	A leather jacket with iron plates sewn in. &
	0,4 &
	4.960\\
	
	Steel Scale Hauberk &
	3 blunt, 6 cutting, 4 piercing, +5 Wound Threshold, 1 cold, 1 hot &
	A leather jacket with steel plates sewn in.&
	0,3 &
	13.270\\
	
	Enchanted Dragonscale Plate &
	+4 Wound Threshold, 4 of every damage type &
	An enchanted plate armor made from dragon scales. Magical. Maximum 10 Agility &
	0,1 &
	1.416.860\\
\end{longtable}


\subsection{Heavy Armor}

Heavy Armor is slow and clunky, but also adds the biggest bonus to armor of any type. It requires several minutes to don and doff such a piece of armor, and reduces the Agility of the wearer to a maximum value.


\rowcolors{2}{lightgray}{white}
\begin{longtable}{p{1.5cm} | p{4cm} | p{2.5cm} | p{1cm} | p{1.5cm}}
	Name & Resistances & Description & Wght & Price\\ \hline
	
	Wood Cuirass &
	2 blunt, 3 cutting, 2 piercing, +3 Wound Threshold, 1 cold, 1 hot, 4 corrosive, 1 electrical &
	This armor is made from wooden plates overlapping each other. Rather clunky. Maximum Agility 6 &
	3,2 &
	400\\
	
	Bone Armor &
	3 blunt, 5 cutting, 4 piercing, +4 Wound Threshold, 1 cold, 1 hot, 5 corrosive, 1 necrotic, 1 radiation, 1 electrical &
	This armor is made from a collection of human bones, and is slightly enchanted with shamanic magic. Maximum Agility 6 &
	2,9 &
	3.380\\
	
	Heavy Brigandine &
	2 blunt, 5 cutting, 4 piercing, +4 Wound Threshold, 3 cold, 3 hot &
	This armor is made from heavy cloth quilted into little pockets. Maximum Agility 8 &
	1,5 &
	4.820\\
	
	Iron Plate &
	4 blunt, 5 cutting, 5 piercing, +5 Wound Threshold, 2 cold, 2 hot, 2 corrosive, 1 necrotic, 1 nihilation, 1 suffocation & 
	A plate cuirass made of hard iron. Maximum Agility 8 & 
	5,6 &
	24.120\\
	
	Steel Plate &
	4 blunt, 6 cutting, 6 piercing, +6 Wound Threshold, 2 cold, 2 hot, 2 corrosive, 1 necrotic, 1 nihilation, 1 suffocation & 
	A plate cuirass made of steel. Maximum Agility 8 & 
	5,3 &
	40.600\\
	
	Enchanted Wyrmscale Plate &
	+6 Wound Threshold, 6 against every damage type & 
	A plate cuirass crafted from a great wyrm's scales. Magical. Maximum Agility 10 & 
	0,4 &
	14.670.000\\
	
	Enchanted Adamantine Plate & 
	+8 Wound Threshold, 8 against every damage type & 
	A plate forged from adamantium. Extremely valuable and durable. Magical. Maximum Agility 8 & 
	1,2 &
	30.147.600\\
\end{longtable}