\subsection{Armor Attributes}

\subsubsection{Warming}
An Armor with this attribute helps against the cold. It grants resistance to cold by the value specified.

\subsubsection{Cooling}
An Armor with this attribute helps against the heat. It grants resistance to heat by the value specified.

\subsubsection{Shielding}
An Armor with this attribute grants damage resistance to Radiation damage by the amount specified.

\subsubsection{Insulating}
An Armor with this attribute grants damage resistance to Electrical damage by the amount specified.

\subsubsection{Living}
An Armor with this attribute grants damage resistance to Necrotic damage by the amount specified.

\subsubsection{Isolating}
An Armor with this attribute helps against temperature. It grants resistance to heat and cold by the value specified.

\subsubsection{Flammable}
An Armor with this attribute easily catches fire. Whenever a character wearing it would take heat damage, the armor starts to burn.\\
Burning Armor can be put out by anyone who is able to touch it. Doing so takes 4 AP.\\
Burning Armor is also extinguished when the wearer would take cold damage, or when it is doused in water.\\
If burning armor isn't put out by some other effect, it burns for 6 AP if it's cloth or light armor, 10 AP if it is medium or 14 AP if it is heavy.\\
While wearing a burning armor, the wearer takes 1 heat damage per AP that passes until it is put out. Any armor that burned for at least 1 AP becomes damaged afterwards, losing all of its properties.

\subsubsection{Horrid}
An Armor with the horrid attribute has dark energies associated with it. When the wearer of such armor takes necrose or psychic damage, they take an additional 3 damage from that damage source.

\subsubsection{Enchantable}
An Armor that has this attribute can be enchanted a different amount than just once. It can instead hold an amount of Enchantments by the number specified. This means that any armor that doesn't have the "Enchantable" attribute specified has the "Enchantable 1".

\subsubsection{Lightweight}
An Armor with the Leightweight attribute reduces the wearer's Agility as if it were one Weight class lower. Additionally, if the wearer of said armor is more proficient in the lower weight class than the armor's actual weight class, he can benefit from the lower proficiency as if the armor was one weight class lower.

\subsubsection{Magic Defense}
An Armor with this attribute grants additional damage resistance to damage from spells, by the amount specified.

\subsubsection{Elemental Defense}
An Armor with this attribute grants damage resistance to elemental damage by the amount specified, if no other aspect of the armor already grants larger resistance to that element.

\subsubsection{Indestructible}
An Armor with this attribute grants damage resistance to Corrosion and Nihilation damage by the amount specified.

\subsubsection{Under}
An Armor with this attribute can be worn under any piece of armor that has the "Over" or "Flexible" attribute.\\
When both armors grant resistances to a damage type or wounds, do not add them together. Instead, the larger respective resistance count.\\
Wearing two pieces of armor reduces a character's Agility by 2, to a minimum of 1.

\subsubsection{Over}
An Armor with this attribute can be worn over any piece of armor that has the "Under" or "Flexible" attribute.\\
When both armors grant resistances to a damage type or wounds, do not add them together. Instead, the larger respective resistance count.\\
Wearing two pieces of armor reduces a character's Agility by 2, to a minimum of 1.

\subsubsection{Flexible}
An Armor with the "Flexible" attribute can be worn over any piece of armor that has the "Under" attribute, or under any piece of armor that has the "Over" attribute. It can not be worn with another piece of armor that has the "Flexible" attribute.\\
When both armors grant resistances to a damage type or wounds, do not add them together. Instead, the larger respective resistance count.\\
Wearing two pieces of armor reduces a character's Agility by 2, to a minimum of 1.