\subsection{Hats and Helmets}\label{subsec:helmets}

\subsubsection{Knight's Helmet}\label{item:knightHelment}
Size: M\\
Price: 100G\\
The knight's helmet is a full metal helmet with a visor.
It reduces the wearer's perception by 2, to a minimum of 1.\\
If the wearer of this helmet is subject to a critical hit from a weapon attack, the attacker must roll a d6.
On a 1, the attack does not deal additional damage from being a critical hit.\\

\subsubsection{Mages' Hat}\label{item:mageHat}
Size: M\\
Prices: 150G\\
The mages' hat is a signifier of a studied magister of magic.
It is pointy and made of magical silk.\\
While wearing a Mages' Hat, the wearer can remember 4 additional spells.\\

\subsubsection{Leather Helmet}\label{item:leatherHelmet}
Size: M\\
Price: 20G\\
The Leather Helmet is a simple cap made of leather, with straps on the sides.\\
If the wearer of this helmet is subject to a critical hit from a weapon attack, the attacker must roll a d12.
On a 1, the attack does not deal additional damage from being a critical hit.\\

\subsubsection{Hood}\label{item:hood}
Size: M\\
Price: 5G\\
This hood protects the wearer's head of wind and rain and makes it more difficult to see their face from the side.\\

\subsubsection{Skullcap}\label{item:skullCap}
Size: M\\
Price: 50G\\
This metal cap hugs the wearer's skull in order to protect it.\\
If the wearer of this helmet is subject to a critical hit from a weapon attack, the attacker must roll a d8.
On a 1, the attack does not deal additional damage from being a critical hit.\\

\subsubsection{Faceless Mask}\label{item:facelessMask}
Size: M\\
Price: 70G\\
This special mask is completely featureless.
It blocks the user's sight, making them effectively blind.
However, it also increases their concentration.
While wearing a faceless mask, the mana costs for spell upkeep is halved.\\
