\chapter{Prayers and Wonders}
This category includes prayers and wonders.\\
A character that has started to follow in the path of divine stewardship will choose one of the four divines as their patron deity. They can then learn prayers and add them to prayer books. Once per day at a certain time, which is also called their deity's divine hour, they can equip prayers by studying their prayer book. These prayers require Piety to be equipped. Piety is gained by performing acts that the characters' deity would enjoy.\\
Some acts, like donating money to the respective church, killing Daemons or performing rites on others, is usually seen positively by all four deities. However, some acts might be seen positively by one deity, but as heretical by a different deity. Which acts provide Piety points is generally in the discretion of the GM.\\
A character can equip as many prayers as their Piety points allow. This means that a character with 10 Piety would be able to equip \nameref{sec:divinePunishment}, \nameref{sec:divineRest} and \nameref{sec:thornShot}.\\
Wonders are a different type of Divine Perk. A character can use one Wonder per day, and doing so reduces their Piety to 0 until they pray at their deities' divine hour again. Wonders don't need to be written in a Prayer book. If a character knows the perk of a Wonder, they can use it whenever they like.\\

	%Prayers

	\input{./perks/perks/divine/divinedisciple.tex}
	
	\input{./perks/perks/divine/prayers/beaconoflight.tex}
	
	\input{./perks/perks/divine/prayers/deathburst.tex}
	
	\input{./perks/perks/divine/prayers/divineenhancement.tex}
	
	\input{./perks/perks/divine/prayers/divinepunishment.tex}
	
	\input{./perks/perks/divine/prayers/divinerest.tex}
	
	\input{./perks/perks/divine/prayers/thornshot.tex}
	
	\input{./perks/perks/divine/prayers/truebalance.tex}
	
	
	%Wonders
	
	\input{./perks/perks/divine/wonders/divinesalvation.tex}
	
	\input{./perks/perks/divine/wonders/divinerejuvination.tex}
	
	\input{./perks/perks/divine/wonders/divinefury.tex}
