\chapter{Odem Perks}\label{ch:odemPerks}
Odem is a strange and mystical power that some people are born with.
It usually lies dormant for a long time, until the person is in emotional or physical distress and it manifests into a psychic burst of energy that harms everyone in their surroundings.
Most people consider Odem to be a curse, and thus many Odem-wielders are enslaved, ostracized, or outright banned from civilized countries.
In order to combat this, the Church of Four has created an elite troupe of hunters called "The Seekers", who are tuned to Odem and can feel it manifest in others.
Those found be the Seekers are usually captured and brought to a monastery, temple or other holy organization, where they recieve a Sigil that suppresses their powers.
Oftentimes, these holy places will then keep the person prisoner.\\
Some Odem wielders have been able to manifest their Odem in the form of coloured flames, each of which has different effects.
These so-called "Dervishes" can summon their flames and invoke powerful effects with them.
However, mastering a flame is difficult, and takes many years of training, meditation and experience.\\
This means that the already acquired levels in one flame perk accumulate, and increase the cost of the next level of flame perk.
This results in the following perk costs:\\
\\
Rank Progression:\\
\\
\begin{minipage}{0.30\textwidth}
    \rowcolors{2}{lightgray}{white}
    \begin{tabular}{l | l}
        Total Flame Rank & Cost\\ \hline
        I & 100\\
        II & 200\\
        III & 400\\
        IV & 700\\
        V & 1,100\\
    \end{tabular}
\end{minipage}
\begin{minipage}{0.30\textwidth}
    \rowcolors{2}{lightgray}{white}
    \begin{tabular}{l | l}
        Total Flame Rank & Cost\\ \hline
        VI & 1,600\\
        VII & 2,200\\
        VIII & 2,900\\
        IX & 3,700\\
        X & 4,600\\
    \end{tabular}
\end{minipage}
\begin{minipage}{0.30\textwidth}
    \rowcolors{2}{lightgray}{white}
    \begin{tabular}{l | l}
        Total Flame Rank & Cost\\ \hline
        XI & 5,600\\
        XII & 6,700\\
        XIII & 7,900\\
        XIV & 9,200\\
        XV & 10,600\\
    \end{tabular}
\end{minipage}

\input{perks/odem/odemcurse.tex}

\input{perks/odem/odemsigil.tex}

\input{perks/odem/redOdemFlame.tex}

\input{perks/odem/blueOdemFlame.tex}

\input{perks/odem/greenOdemFlame.tex}