\chapter{Calendar and Zodiac Signs}
\section{Calendar}
The Kusaen Calendar comprises of 13 months with an additional week to end the year. Each Month comprises of 3 weeks, each of which has 10 days.\\
During the last week, which is the end of the Kusaen year, a total eclipse occurs, keeping the planet dark for 10 days. People generally keep in their houses and towns during this time, fearing an increased amount of demonic influence outside. Most of the fall and winter is spent preparing for this one week.\\
\subsection{Weekdays}
\begin{enumerate}
	\item Tharday
	\item Felday
	\item Trilday
	\item Thormday
	\item Pakday
	\item Solday
	\item Khulday
	\item Restday
	\item Massday
	\item Hearthday
\end{enumerate}


\subsection{Months}
\begin{enumerate}
	\item Deepwinter
	\item Thawflight
	\item Showerhome
	\item Blossombreak
	\item Sunrealm
	\item First Harvest
	\item Fairterm
	\item Second Harvest
	\item Leaffall
	\item Last Harvest
	\item Gods' Rest
	\item Darkfall
	\item Coldheart
	\item (Week of Darkness)
\end{enumerate}


\section{Zodiac Signs}
There's 10 Zodiac Signs for the Kusaen Planet, changing every 39 days. During the Week of Darkness, there are no stars visible in the sky above, meaning that those born in this time carry the "Fateless" Zodiac sign. Each of these acts as a special, active perk that can be chosen at the beginning of the game. After using this Perk, a character has to wait 24 hours before being able to use it again.\\

\begin{enumerate}
	\item \textbf{The Horseman}: 1. Deepwinter - 9. Thawflight
	\item \textbf{The Worker}: 10. Thawflight - 18. Showerhome
	\item \textbf{The Cave}: 19 Showerhome - 27.Blossombreak
	\item \textbf{The Crown}: 28. Blossombreak - 6.First Harvest
	\item \textbf{The Hero}: 7. First Harvest - 15. Fairterm
	\item \textbf{The Eagle}: 16. Fairterm - 24. Second Harvest
	\item \textbf{The Mountain}: 25. Second Harvest - 3.Last Harvest
	\item \textbf{The Ship}: 4. Last Harvest - 12.Gods' Rest
	\item \textbf{The Quill}: 13. Gods' Rest - 21. Darkfall
	\item \textbf{The Flower}: 22. Darkfall - 30. Coldheart
	\item \textbf{The Fateless}: 1. Week of Darkness - 10. Week of Darkness
\end{enumerate}


\input{./perks/perks/zodiacHorseman.tex}
\input{./perks/perks/zodiacWorker.tex}
\input{./perks/perks/zodiacCave.tex}
\input{./perks/perks/zodiacCrown.tex}
\input{./perks/perks/zodiacHero.tex}
\input{./perks/perks/zodiacEagle.tex}
\input{./perks/perks/zodiacMountain.tex}
\input{./perks/perks/zodiacQuill.tex}
\input{./perks/perks/zodiacShield.tex}
\input{./perks/perks/zodiacFlower.tex}
\input{./perks/perks/zodiacFateless.tex}