\section{Attributes}\label{sec:stats}
There are seven main attributes in the RLP:\\

\textbf{Strength (ST)}\label{stat:strength} describes a character's muscle strength.
It's an important ability for melee combat, and determines carrying capacity.\\


\textbf{Vitality (VI)}\label{stat:vitality} is a character's bodily defensive ability.
It determines how a character is able to withstand extreme weather conditions, sickness or poison.\\


\textbf{Dexterity (DE)}\label{stat:dexterity} describes a character's hand-eye-coordination.
It's important with fine tasks like crafting or disabling traps, picking pockets and locks or tying knots.
It also helps with ranged or melee combat, depending on the attacker's weapon.\\


\textbf{Agility (AG)}\label{stat:agility} is a character's ability to act when necessary, and also describes how a character is able to move around.
It's important for climbing, swimming, running, sneaking, gymnastics and tumbling in general.\\


\textbf{Intellect (IN)}\label{stat:intellect} describes a character's overall rational ability, his memory and his ability to acquire knowledge.
It can also be used to describe a character's overall knowledge about a specific topic or lore.
It's also important for magic users.\\


\textbf{Perception (PE)}\label{stat:perception} is a character's ability to realize his surroundings.
It's important for battle, but also necessary to survive while exploring dangerous environments.
It's also important for social encounters.\\


\textbf{Empathy (EM)}\label{stat:empathy} describes a character's ability to understand others.
It's important for most social encounters, and determines how easy it is for a character to haggle prices, to talk himself out of a battle or seduce a barmaid.\\
Each of these attributes are described as a value of 1--12, with 4--7 being average values.
A character with a 2 in Empathy may not even be able to articulate a thought, while a character with an 11 in Empathy is able to persuade even kings.