\section{Guard}\label{background:guard}
Before working as an adventurer, you were a guard, part of a militia, or a member of law enforcement.
You might have worked as a regular city guard, patrolling the streets and protecting the citizens from petty criminals.
Or maybe you worked as part of a militia, possibly of a smaller town, and defended your home against wild animals and monsters.
Possibly, you worked as part of a police force, and solved crimes.

\subsection{Statistics}
Choose either Deception, Intimidation, or Negotiation.
You gain a +1d4 experience bonus on checks regarding this type of interaction, as well as Examination.

\subsection{Adventuring Hook and Goal}
You might have been sent to capture a dangerous fugitive that has fled from prison.
If you were part of a small town militia, maybe someone sent you on a mission to save the village from a threat or illness.
Or you have found an item that needs to be moved away, to protect your home.
As a guard in a larger city, you might have been framed for a crime that was committed by a corrupt politician or other guard, and now you're sent into exile until you can redeem your good name.
Possibly, you made a mistake and cost the live of someone you were working with, or protecting - and now you can't work in the field anymore.
It might be that an old, unsolved crime has come to haunt you, or a certain private patron has hired you off the force with an offer too good to refuse.
Or maybe you quit your guard job to become a private investigator in a large city, and are working on that one fateful case.