\section{Odem Wielder (Captured)}\label{background:odemWielderCaptured}
You are born with the Curse of Odem.
This means, that our emotions can manifest themselves into violent outbursts, that deal psychic damage against people around you.
As a captured Odem Wielder, the Seeker Guild has found you after one of your outbursts, taken you into custody, and placed a sigil somewhere on your body - a sigil that is supposed to help you gain control over your emotions.
They then put you into either a monastery, or a military organization with religious undertones (like the Order of the Copper Spear), where you grew up further.

\subsection{Statistics}
You start the game with 1 Perk Rank in~\ref{perk:odemCurse},~\ref{perk:odemSigil} and gain a +1d4 experience bonus on checks regarding lore (religion).

\subsection{Adventuring Hook and Goals}
Maybe you have escaped the place where you were captured, and are now on the run.
You know that, whenever your Odem triggers an outburst, the Seeker Guild will be on your heel again.
Alternatively, you were sent out by the order you live in, to fulfill some task or run some errand, when adventure strikes, and you take the opportunity to make your own path.
It could also happen that the fort or monastery where you grew up was destroyed by some outside force, and you were able to survive somehow.
You probably don't want to be taken in by the Seeker Guild anymore, so learning to control your Odem (maybe after breaking the sigil somehow) should be your first priority.
Additionally, you know that the Seeker Guild isn't allowed to operate in certain places - there are sanctuaries for people with the Odem Curse, and old masters that learned to control it that might be able to teach you.
But finding these places and people will be dangerous, and the Guild is already on your tracks.