\section{Divine Disciple}\label{perk:divineDisciple}
\textbf{Cost:} 100 CP\\
\textbf{Requirements:} - \\
\textbf{Passive, Repeatable}\\
You are a disciple of one of the Four - Avior, Ebron, Prak or Irani.
You gain 5 Piety Points.
Once during Dawn for Irani, Midday for Avior, Dusk for Ebron or Midnight for Prak, you can pray to prepare and equip Prayers you know from your prayer book.
Every prayer needs a certain amount of Piety Points.
You can equip higher ranks of a prayer only if you equip the lower ranks.
You can freely use equipped Prayers.
You can also learn and use Wonders.
Using a Wonder reduces your total Piety Points by a certain amount until you are able to prepare and equip prayers again.
If this reduction puts your current Piety Points below the total needed for your prayers, you automatically unequip enough prayers of your choice (keeping the rank requirements in mind) until they fit again.\\
\\
\begin{itemize}
\item \textbf{Avior} \\
Avior is the god of humankind, civilization, huntsmen, war, farming, the sun and the hearth.
Avior favors humans, especially innocents and children, as well as Soldiers and holy warriors of all races.
Avior hates daemons, evil humanoids (like Goblins, Orcs etc.), and beasts.

\item \textbf{Ebron}\\
Ebron is the god of travel, merchants, justice, dragons, time and balance.
Ebron favors dragons, slaves, fay, elves, iganians, and wielders of the Odem-flame.
Ebron hates daemons, blood mages, criminals, and creatures from the far realms.

\item \textbf{Prak}\\
Prak is the god of noblemen, guardian of death, the creator of magic and the god of craftsmen.
Prak favors artisans, magicians, and rightful leaders.
Prak hates daemons, blood mages, the undead (as well as necromancers), and claimless usurpers.

\item \textbf{Irani}\\
Irani is the godess of nature, the ocean, womanhood, birth, freedom and crime.
Irani favors women and children, beasts, shamans and druids, fairy creatures and criminals.
Irani hates daemons, blood mages, tyrannical leaders, those that defile nature, lycanthropes and those that harm women.
\end{itemize}
\\
You gain Piety Points by performing certain activities.\\
You gain one additional piety point whenever you pay 100 Gold to an organization of your Diety.\\
You gain one Piety Point whenever you and your allies defeat strong creatures that are one of the hated creatures of your deity.\\
You gain two Piety Points whenever you defend someone who is favored by your deity.\\
You gain one Piety Point for major rituals that you perform acting as a cleric for your Deity - such as overseeing a trial for Ebron, performing a coronation for Prak, blessing an army for Avior, or performing a wedding for Irani.\\
You gain up to 3 additional Piety Points for performing major tasks that help or protect your faith, a holy site of your faith, or further your gods' agendas.\\
This might include performing great acts of heroism (like a Disciple of Avior defeating a crazed Dragon that was terrorizing the townspeople, a Disciple of Irani helping in bringing down a tyrannical leader, or a Disciple of Ebron helping in solving a mass murder)
\\
You can choose to take this Perk again.
However, the cost doubles for each time you take it.
When you do so, you lose all Piety Points and chose a different deity as your new Patron deity.