\chapter{Damage Types}\label{ch:damageTypes}

\section{Physical Damage Types}\label{damagetypes:physical}

\rowcolors{2}{lightgray}{white}
\begin{longtable}{l p{5cm} p{5cm}}
Type & Description & Healing \\ \hline
blunt  & Damage dealt by blunt trauma to the body, usually from round rocks, hammers, clubs or the like. & Healing magic, drinking a healing potion or being bandaged. \\
cutting & Damage dealt from sharp objects, like the edge of a knife or a sharp rock. & Healing magic, drinking a healing potion or being bandaged. \\
piercing & Damage dealt from a pointy object, like a needle, a thrust from a weapon or an arrowhead. & Healing magic, drinking a healing potion or being bandaged. \\
\end{longtable}

\section{Non-Physical Damage Types}\label{damagetypes:nonphysical}

\rowcolors{2}{lightgray}{white}
\begin{longtable}{l p{5cm} p{5cm}}
Type & Description & Healing \\ \hline
cold & Damage from enduring cold climates or being frozen. & Healing magic, drinking a healing potion or being bandaged. Also hot damage reduces a cold wound by the amount taken. \\
heat & Damage from enduring hot climates or from being burnt. & Healing magic, drinking a healing potion or being bandaged. Also cold damage reduces a hot wound by the amount taken. \\
electrical & Damage from electrical current. & Healing magic or drinking a potion. \\
corrosive & Damage from being subject to highly acidic or basic matter. & Healing magic, drinking a healing potion or being bandaged. \\
necrose & Damage from dead tissue being connected to the body. & Healing magic, drinking a healing potion or being operated. \\
radiation & Damage from radiation, causing cancerous tissue to form. & Healing magic or drinking a potion. \\
nihilation & Damage from tissue being annihilated. & Healing magic or drinking a potion. \\
suffocation & Damage from being unable to breathe for too long, be it from drowning, being inside of non-breathable gas or being in a small area with no fresh air flow for too long. Can only wound the Torso. & Wounds from suffocation usually subside after a minute of breathing normally again. \\
psychic & Emotional trauma caused by horror, damaging illusion spells or other forms of emotional scarring. Can only wound the head. & Therapy, healing magic. \\
\end{longtable}

\section{Misc. Damage Types}\label{damagetypes:misc}

\rowcolors{2}{lightgray}{white}
\begin{longtable}{l p{5cm} p{5cm}}
Type & Description & Healing \\ \hline
Stamina & Stamina damage causes a character's Stamina to be reduced, as if it was spent & See "\nameref{subsec:recoverStamina}" \\
Mana & Mana damage causes a character's Mana to be reduced, as if it was spent & See "\nameref{subsec:recoverStamina}" \\
AP & In certain situations, a character becomes dazed for a short while. In this situation, they take AP damage. They are unable to act for a certain amount of time, but can still react normally. Instead, their last action takes longer. AP damage is spent before regular AP. & Usually just waiting\\
Attribute & Some effects reduce a character's Attributes. This normally is a temporary change, or is bound to the effect (For example, the attribute reduction from wounds is bound to the wound that caused it) & Ending the causing effect, or time. 1 Point of Attribute damage is healed per hour. The character can choose which one.\\
Mnemonic & Mnemonic damage represents damage to a character's memory. A character whose memory gets damaged temporary loses an amount of memorized spells equal to the damage dealt. This is usually bound to an effect. & Either the causing effect ending or it heals over time.\\
\end{longtable}
