\section{Daevan Culture}\label{culture:daevan}
You were raised in Daevan Culture.
Daevana usually live as nomads in frozen tundras and taigas, hunting Mammoths, Aurochs and Giant Deer to sustain themselves.
The build huts and yurts from bone and leather, and drink the milk of the few beasts of burden they raise.
Daevan culture in general knows of three different occupations: hunter, warrior, and wise person - with the former two being performed by the same people, just in different times.
Daevana live in small tribes, and try to bother no settled civilizations, but their relative peacefulness to their neighbours is an illusion best not tested.
A Daevan tribe whose hunting grounds are being trodden on by "city-folk" is a dangerous foe indeed.
Daevana follow Irani, one of her children, or a shamanistic faith in the form of Nature-Spirits and/or Ancestral Spirits.
As a result, every tribe has a totem that is their symbol.
A tribe is lead by some form of singular chief or leader, chosen either by bloodline, by the former leader, by popular vote, or by the Wise Person of the tribe.
The wise person is usually some kind of alchemist, shaman, priest or druid in charge of the spiritual and bodily health of the members of the tribe, and acts as a councillor to the chief.
It is not unheard of, that Daevan tribes find friendship with other peoples, even far away ones, since they enjoy trade, telling stories, and are open to other ideas, as long as they don't threaten their way of life.
There are even stories of non-Daevana, usually Whitlan Humans, living as part of Daevan tribes.