\section{Alchemical Recipes}\label{sec:alchemicalRecipes}
Alchemical recipes are organised by Tiers.
Potions are crafted in batches.
You can create up to 5 potions in one batch, and crafting one batch takes one hour.
The potions in a batch all have to be of the same kind.
Crafting potions requires a mortar and pestle.
Each potion requires one set of ingredients and a solvent.
Also, it is necessary to use a vial to create a potion.
If the solvent is already in a vial, no additional vial is necessary.
Each 1-hour batch is created by rolling the check only once. 
The first bonus is applied when the Difficulty Value of that recipe is beaten by 5, and the second bonus is applied when the Difficulty Value is beaten by 10. 
If the check is failed by 5 or more, the creation fails and all the ingredients are lost.
Otherwise, the creation fails and 1 hour passes, but the creator keeps the ingredients.
Creating a potion requires some way of heating it.\\


\subsection{Tier 1 Potions}
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | p{2.5cm} | l | l | p{1.5cm} | p{1.5cm} | p{1cm} }
	Potion & Ingredients & Solvent & DV & 1st Bonus & 2nd Bonus & Recipe Price (In Gold)\\ \hline
	Antidote & 1x Poison Essence I, 1x Health Essence I & Alcohol & 14 & +5 instead & +6 instead & 50\\
	Health Potion & 1x Health Essence I & Water & 12 & +1 health & +2 health & 50\\
	Mana Potion & 1x Magic Essence I & Alcohol & 12 & +1 Mana & +2 Mana & 50\\
	Stamina Potion & 1x Speed Essence I & Fat & 12 & +1 stamina & +2 Stamina & 30\\
	Spider Venom & 1x Spider Venom Sack & Alcohol & 14 & DV 13 instead & DV 14 instead & 30\\
\end{longtable}