\twocolumn
\section{Arcana Rune}
\textbf{Cost:} 50 CP\\
\textbf{Requirements:} -\\
\textbf{Rune, Weapon, Active, Repeatable, Source (50 Gold)}\\
You have mastered the Arcana Rune. It is associated with the basic flow of magic and manifests into an elemental force that is neutral of every element. While Arcana seems to be a very simple Rune, especially for new Apprentices, it has many strong powers and enjoys synergies with other Elements, allowing it to be used in a multitude of Spells.\\
\subsection{Level 1 Abilities}

\subsubsection{Arcane Bolt}
For 4 AP and 3 Mana, you create a bolt of magic out of thin air and hurl it towards an enemy. Make a ranged magic weapon attack. The bolt deals 2d4 piercing damage. You can divide these Weapon Damage Dice onto multiple bolts, each of which requires its own additional weapon attack roll.

\subsubsection{Feel Arcane Energy}
Thanks to your attunement with the arcane energies, you can feel the presence of magic. Any form of the Arcana Rune slightly starts glowing when it touches some magical item, unless that item is shielded from such detection in some form.

\subsection{Level 2 Abilities}
\textbf{Cost:} 500 CP\\
\textbf{Source:} 350 Gold
\subsubsection{Enhanced Arcane Bolt}
You can now use 6 Mana to create an Arcane bolt that deals 4d4 points of damage. You can divide these damage dice between up to 4 bolts, each of which requires its own weapon attack roll.

\subsubsection{Arcane Blast}
You can create a blast of magic energy at a point in a range of \passus{9} around you. This takes 6 AP and 10 Mana. Any creature in an a radius of \passus{3} around your chosen point takes 4d6 blunt damage and must make a Strength check, contested by your Intelligence Check. If they fail, they are pushed \passus{1} away from the point of origin of the blast, and fall prone.

\subsubsection{Feel Lingering Magic}
Your attunement to the magical energies around you have become stronger. Now your Arcana Rune also starts glowing in an area where magic has been cast recently. For every point of Mana spent in an area, the lingering aura lasts for an additional 10 minutes.

\subsection{Level 3 Abilities}
\textbf{Cost:} 1,000 CP\\
\textbf{Source:} 650 Gold
\subsubsection{Arcane Bolt}
You can now use 9 Mana to create an Arcane Bolt that deals 6d4 points of damage. You can divide these damage dice between up to 6 bolts, each of which requires its own weapon attack roll.

\subsubsection{Strong Arcane Blast}
You can now create a stronger arcane blast. The range in which you can choose its point of origin has increased to \passus{12} and the radius of the blast itself has increased to \passus{5}.\\
Additionally, you can now expand 20 Mana instead to deal 10d6 blunt damage.

\subsubsection{Arcane Sight}
You now have the ability to see magical energies circulating around you. In order to do so, you must close your eyes and spend 1 Mana per Action Point. Magical Energies swirl around the Universe like a web or radiation, allowing you to discern shapes of creatures and objects. This type of Sight detects invisible creatures and is nearly 360 degrees.
\onecolumn