\section{Light Rune}\label{rune:light}
\textbf{Cost:} See Runes\\
\textbf{Requirements:} -\\
\textbf{Rune, Weapon, Active, Repeatable, Source (See Runes)}\\
You have mastered the Light Rune.
Light is the element of sight and vision.
It allows sight and brings truth into dark places.
Those that wander in the path of the light never have to watch their step, as they are always on the right path.

\subsection{Rank I Abilities}

\subsubsection{Orb of Light}
For 3 AP you can create a small Orb of Light that shines a bright light for a radius of \passus{4}.
Beyond that, the light fades into dim light for a radius of \passus{4}.
Beyond that, darkness still prevails.
The Orb is the size of your hand and you can control its position telepathically.
However, it can not move further away than \passus{10} from you.
You can decide the colour of the orb and change it at any time. \\
Keeping the Orb of Light up costs 1 Mana per 10 Minutes.


\subsection{Rank II Abilities}

\subsubsection{Spirit of Light}
Your Orb of Light has become a small manifestation of elemental light that follows you around.
It now shines bright light for \passus{6} and dim light for an additional \passus{6}.\\
Additionally, it can now carry coin-sized objects.
However, while carrying such objects it requires 1 Mana per AP.

\subsubsection{Light Burst}
You can now create a burst of light from the Light Rune you are wielding.
Doing so takes 2 AP and 15 Mana.
In a \passus{4}-long cone in front of you, a burst of bright light comes forth.
All creatures in that area must make a Vitality Check against your Intelligence Check.
If they fail, they become blinded for 1D4 + 2 AP.

\subsection{Rank III Abilities}

\subsubsection{Vestige of Light}
Your Spirit of Light can now engulf any creature of your choice within range, making it more difficult to hit it with an attack.
While engulfing a creature in this way, the Dodge of that creature is increased by your Intelligence, but only against attackers that rely on sight.
Doing this costs 3 Mana per AP.

\subsubsection{Daylight Burst}
Your Light Burst has become powerful enough to damage creatures.
Performing a Daylight Burst costs 30 Mana instead of 15, and the cone has a size of \passus{6}.
Any creature inside the cone takes 4D6 Hot damage in addition to having a chance of being blinded.
Undead take 8D6 Hot damage instead.
Vampires take 12D6 Hot damage instead.

\subsubsection{Kaleidoscope}
You can create a burst of colours around you, dazzling and confusing each creature in the area.
Any creature in a radius of \passus{6} around you must make a Perception Check contested by your Intelligence Check.
If a creature fails, they are affected by a random Condition for 2D6 + your Intelligence AP.\\

\rowcolors{2}{lightgray}{white}
\begin{tabular}{r | l || r | l}
	1DX & Condition & 1DX & Condition\\
	\hline
	1 & Entranced & 5 & Unconscious \\
	2 & Frightened & 6 & Enraged \\
	3 & Sleeping & 7 & Calmed\\
	4 & Paralyzed & 8 & Now your ally \\
\end{tabular}